Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-01-09 src/tex/ms.tex
[showyourwork] overleaf sync

\paragraph{Mock Observational Data}
Our analysis uses mock observations drawn from the \textit{neural network} emulator with fixed values of the global galactic parameters $\alpha_{\rm IMF}=-2.3$ and $\log_{10}(N_{\rm Ia})=-2.89$ and the local parameters $\vec{\Theta}_i$ from Tab. \ref{tab:priors}, additionally drawing $T_i$ uniformly in the range $[2,12.8]$ Gyr, to minimize overlap with the neural network training birth-time limits when observational uncertainties are included. 
Each set of parameters is passed to the NN, producing eight true chemical abundances, to which we add a Gaussian error of $0.05$ dex.
The outcome of this mock data creation is a set of 1000 stars \textcolor{red}{we vary this number, right?}, emulating a real dataset.

>>>>

\paragraph{Mock Observational Data}
Our analysis uses mock observations drawn from the \textit{neural network} emulator with fixed values of the global galactic parameters $\alpha_{\rm IMF}=-2.3$ and $\log_{10}(N_{\rm Ia})=-2.89$ and the local parameters $\vec{\Theta}_i$ from Tab. \ref{tab:priors}, additionally drawing $T_i$ uniformly in the range $[2,12.8]$ Gyr, to minimize overlap with the neural network training birth-time limits when observational uncertainties are included. 
Each set of parameters is passed to the NN, producing eight true chemical abundances, to which we add a Gaussian error of $0.05$ dex.
\textcolor{red}{here goes the assumption that stars are iid since each stars is produced by a single call to chempy. However, real physics might correlate stars abundacnes by star formation histories and cumulative enrichment...}
The outcome of this mock data creation is a set of 1000 stars \textcolor{red}{we vary this number, right?}, emulating a real dataset.
